When are Fuzzy Extractors Possible?

### 2014-10-04 info-bounds/FuzzyExtPossibility.tex
notation run through

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\key}{\ensuremath{\class{key}}\xspace}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\crust}{\ensuremath{\class{Crust}}\xspace}
\newcommand{\inter}{\ensuremath{\class{Inter}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}
\newcommand{\eqdef}{\stackrel{\rm def}{=}}

@@

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \le \Hfuzz(W) \le \Hoo(W)-\log |B_t(\cdot)|$ with equality when $t=0$.

Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have roughly the same probability.  We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.

@@

The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.  The result for fuzzy extractors is more delicate.  It requires the fuzzy extractor to correct $t = \omega(n^{1/2}\log n)$ errors~(where $n$ is the length of the string) and have perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem.
This result also relies on the majority of points lying near boundaries of a set. Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

\subsection{Sufficiency of $\Hfuzz$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

@@

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
 Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
%\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

@@

\begin{definition}
Let $\mathcal{M}$, $\chi$ be finite sets.
A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):%If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal:
%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{proposition}
\label{prop:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result)
Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.

@@

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w,w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume distribution-aware algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) distribution-aware constructions of sketches and extractors is an interesting problem.

\section{Sufficiency of $\Hfuzz$ for Distribution-Aware Algorithms}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.

@@

\begin{definition}
Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
\end{definition}

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\key}{\ensuremath{\class{key}}\xspace}
\newcommand{\Key}{\ensuremath{\class{Key}}\xspace}

\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\crust}{\ensuremath{\class{Crust}}\xspace}
\newcommand{\inter}{\ensuremath{\class{Inter}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}
\newcommand{\eqdef}{\stackrel{\rm def}{=}}

@@

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$ with equality when $t=0$. \bnote{I don't follow this equation, equality also for well-spread distributions}

superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

This characterization justifies $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have roughly the same probability.  We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.

@@

The result for fuzzy extractors is delicate.  The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem.
The result also relies on the majority of points lying near boundaries of a set. Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

Second, we can weaken the computational assumption necessary for $\Hfuzz(W)$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

@@

\section{Preliminaries}
\label{sec:preliminaries}
%For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
 Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

The {\em min-entropy} of $W$ is $\Hoo(W) = -\log(\max_w \Pr[W=w])$,
and the {\em average (conditional)} min-entropy of $W$ given $P$ is  $\Hav(W|P) = -\log(\expe_{p\in P} \max_{w} \Pr[W=w|P=p])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   Let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
%\end{definition}

The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.  If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = \key] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

@@

\begin{definition}
Let $\mathcal{M}$, $\chi$ be finite sets.
A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(\tilde{m}, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
$\tilde{H}_\infty(X|Y) \ge \tilde{m}$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):%If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal:
%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.

@@

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume distribution-aware algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) distribution-aware constructions of sketches and extractors is an interesting problem.

\section{Sufficiency of $\Hfuzz(W)$ for Distribution-Aware Algorithms}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.

@@

\begin{definition}
Let $F : \mathcal{K} \times \mathcal{M} \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in \mathcal{M}$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
\end{definition}
